\chapter{Recreational Mathematics}
\label{chap:recreationalMathematics}
It is important to understand what recreational mathematics is in order to get a better understanding of the Rubik's cube. This chapter presents a definition of recreational mathematics and a few examples of recreational mathematical puzzles other than the Rubik's cube.
\section{Definition}
Recreation means to do something which is amusing or relaxing. Mathematics is somewhat harder to give a precise definition, due to the vast amount of subjects that fall under this term. Most people do however have a common idea what mathematics is.

Recreational mathematics is hereby defined as mathematical problems, puzzles or games which are fun and interesting to common people. \cite{Singmaster98} \cite[18]{Trigg78}
\section{Puzzles}
This project is dedicated to the Rubik's cube and the cube will be covered in detail later in this report. This section will instead describe some puzzles related to the Rubik's cube.
\subsection{Magic Square}
\label{sec:magicSquare}
%((INDSÆT FORKLARING AF HVAD MAGIC SQUARE ER HER))
The Magic Square origins from ancient China. It was said that the people near the river Lo made offerings. Every time they made an offering a tortoise emerge from the river. On the back of the tortoise there was said to be a Magic Square.

The Magic Square from this tale was a 3 order normal magic square. This is not the only order in which a magic square can be created; it is possible to make an ``$n$'' order normal magic square. Although it has been proven that it is not possible to make a second order magic square.

In order to solve the Magic Square, it is needed to know the magic constant -- the constant which every row, line and diagonal adds up to for the given order $n$. This constant can be computed with the formula in \ref{align:magicConstant}.

\begin{align}
\label{align:magicConstant}
	M(n) = \frac{n \cdot (n^2+1)}{2}
\end{align}

The proof of this formula is quite straight forward. As the table \ref{tab:magicSquareOrder3} illustrates, a Magic Square of the order 3 contains the numbers from 1 to 9. Generally a Magic Square of the order $n$ contains the numbers from 1 to $n^2$.

The sum of the numbers of a row in a Magic Square is equal to the magic constant. If the magic constant is multiplied by the order $n$ it would be equal to the sum of alle the integers, since each number only occurs once in a Magic Square.

\renewcommand{\arraystretch}{1.3}
\begin{table}
	\centering
		\begin{tabular}{|c|c|c |@{\vrules}| c|}
			\hline
			6&1&8&15 \\
			\hline
			7&5&3&15 \\
			\hline
			2&9&4&15 \\
			\noalign{\hrules}
			15&15&15&45 \\
			\hline
		\end{tabular}
	\caption{\myCaption{A Magic Square of the order 3, by adding the three numbers in any row, column or diagonal, the magic constant is seen to be 15}}
	\label{tab:magicSquareOrder3}
\end{table}

\begin{align}
\label{proof:magicConstant1}
	n \cdot M \left( n \right) = \sum ^{n^2}_{i = 1} i = 1 + \cdots + n^2
\end{align}

The equation \ref{proof:magicConstant1} can be rewritten into the equation \ref{proof:magicConstant2}(See proof of the right hand side transcription in appendix X).

\begin{align}
\label{proof:magicConstant2}
	n \cdot M \left( n \right) = \frac{n^2 \cdot \left( n^2 + 1 \right)}{2} \\
\label{proof:magicConstant3}
	M \left( n \right) = \frac{n \cdot \left( n^2 + 1 \right)}{2} 
\end{align}

The equation \ref{proof:magicConstant3} shows the function which gives the magic constant for a Magic Square of the order $n$.
	\input{input/introduction/recreationalMathematics/magicCube}
	\input{input/introduction/recreationalMathematics/magicPuzzle}

