\chapter{Discussion}
\myTop{Something something of something discussion}





\section{Another Language}

\input{input/epilogue/discussion/comparison}

\section{Improving the Algorithms}

\subsection{Kociemba's Algorithm}
Write about the following improvements:

When the cube is solved to H it is possible to look at it from other angels. Secondary as primary and tertiary as primary.
Both the move into H and in H could be saved in a lookup table to increase the speed.
Cloning the cube, to make the program multithreaded.
Running the program on a x64 bit processer has a lot of influence on the program. 

\subsection{Beginner's Algorithm}
%%%BLA BLA BLA read beginner's first etc.

When describing the improvement of the beginner's algorithm, only improvements are described step by step. 
A twist sequence which leads to the next step may be the most efficient for doing just that, but can potentially cause the entire twist sequence from the scrambled state to the solved state to be longer. 
i.e. a long partial twist sequence may lead to a shorter overall twist sequence. In order to utilize this a lot of analysis is necessary, which is nearly impossible for a person to perform and would take a very large amount of programming to implement.


The beginner's algorithm is as mentioned before a very twist-wise inefficient solving algorithm. 
There are however quite a few areas in which the algorithm can be improved.
First of all choosing the right face to be the face of the first layer will decrease the number of twists needed to complete the first step.




