\section{Permutations}
\label{sec:permutations}
%To calculate how many positions the cube can be placed in, we have to look at the general cube terminology in section \ref{sec:generalNotation}
In this section the number of permutations of the \rubik{} will be calculated \cite{rokicki09}. 
The first corner \cpiece{} can be placed in one of eight \cubicle{}s, the next corner \cpiece{} can be placed in one of the seven remaining \cubicle{}s. %, since we already use 1, and so on.% 
This means that the corner \cpiece{}s can be placed in $8\cdot7\cdot6\cdot5\cdot4\cdot3\cdot2\cdot1=8!$ positions. 
%Now the 8 corner \cpiece{}s are placed at the right position. 
This does not mean they have the correct orientation since a corner \cpiece{} has three different \facelet{}s and therefore three different possible orientations. 
This means there are $3^8$ orientations of the eight corner \cpiece{}s, which yields $8!\cdot3^8$ corner permutations. 


The 12 edge \cpiece{}s can be placed in 12 different \cubicle{}s and every edge \cpiece{} can be orientated in two different ways. 
This yields $2^{12}$ different orientations and $12!$ different positions of the edge \cpiece{}s. 
This gives us $2^{12}\cdot12!$ different edge permutations. 

All of these corner and edge permutations adds up to a total of 
\begin{equation*}
3^8\cdot2^{12}\cdot12!\cdot8!=519,024,039,293,878,272,000 \approx 5.2\cdot10^{20} \text{ permutations.}
\end{equation*}
There are however some limitations to a correctly assembled \rubik{}. 
Only seven out of the eight corner \cpiece{}s can be orientated independently. 
The last corner \cpiece{}'s orientation is directly dependent on the other corner \cpiece{}s. 
The same logic applies to the edge \cpiece{}s, which means that only 11 edge \cpiece{}s can be orientated independently.
Furthermore the orientation of the edge \cpiece{}s is also dependent on the orientation of the corners, which halves the number of possible permutations.

The legitimate \rubik{} has 
\begin{equation*}
3^7\cdot2^{10}\cdot12!\cdot8!=43,252,003,274,489,856,000\approx 4.3\cdot10^{19} \text{ permutations.}
\end{equation*}