\section{Class Interaction}
\myTop{}
\subsection{The Cube Class}
The cube class creates the 20 \cubicle{}s in which the \cpiece{}s can be positioned. Furthermore the cube class creates the faces and \cubie{}s. The class also gives each \cpiece{} its \facelet{}s. The \cubie{}s are then put into a \face{}. The cube class creates six \face{}s -- two primary, two secondary and two tertiary faces. Each type of \face{}s are placed opposite to each other. e.g. the up and down faces are both primary.
\subsection{The Face Classes}
The \face{} class takes cubicles from the cube class and position them in a clockwise order. Furthermore the \face{} class takes a face color from the cube class and gives it to a face. In addition the \face{} class makes two methods that twist a face clockwise or counterclockwise.

There are three different types of \face{}s; primary \face{}s, secondary \face{}s, and tertiary \face{}s.
Each type has its own class, which inherits from the \face{} class.
The reason for the different classes is that there is a different in how the orientation of the \cubie{}s changes depending on what type of \face{} being \twist{}ed.
Orientation of \cubie{}s will be covered in ref\{orientation\}.
\subsection{The Cubicle Classes}
%Måske noget om cubicle class, hvis der bliver lavet noget.
The corner \cubicle{} class creates a \cubicle{} either with or without a corresponding corner \cpiece{}. The edge \cubicle{} class has the same properties, just with an edge \cubicle{}.
\subsection{The Cubie Classes}
The \cpiece{} class sets the orientation correctly by default, and it has functions that return the orientation and \facelet{}s of the \cpiece{}. The corner and edge \cpiece{} classes have functions which return the orientation of the \cpiece{}.
\subsection{The Facelet Class}
The \facelet{} class contains the color of a \facelet{}.
\myTail{}