\chapter{Recreational Mathematics}
\label{chap:recreationalMathematics}
\myTop{It is important to understand what recreational mathematics is in order to get a better understanding of the \rubik{}. The \rubik{} is related to other recreational mathematical puzzles, which have inspired the \rubik{} and are simpler to understand at first grasp. This chapter presents a definition of recreational mathematics and a few examples of recreational mathematical puzzles other than the \rubik{}. Different theorems for these puzzles are presented and proved, because similar proofs are used later for the \rubik{}.}

\section{Definition}
Recreation means to do something which is amusing or relaxing. Mathematics is somewhat harder to give a precise definition of due to the vast amount of subjects that fall under this term. Most people do however have a common idea of what mathematics is. So for the purpose a definition of mathematics, each reader may use his or her own.

Recreational mathematics is hereby defined as mathematical problems, puzzles or games which are fun and interesting to laymen as well as mathematicians. \cite{Singmaster98} \cite[18]{Trigg78}
\section{Puzzles}
This project is dedicated to the \rubik{} and the cube will be covered in detail later in this report. This section will instead describe some puzzles related to the Rubik's cube.

	\input{input/introduction/recreationalMathematics/magicSquare} %input/introduction/recreationalMathematics/magicSquare %Denne sti skal bruges når rapporten samles!
	\input{input/introduction/recreationalMathematics/magicCube} %input/introduction/recreationalMathematics/magicCube %Denne sti skal bruges når rapporten samles!
	\input{input/introduction/recreationalMathematics/magicPuzzle} %input/introduction/recreationalMathematics/magicPuzzle %Denne sti skal bruges når rapporten samles!
\myTail{This chapter has given a definition of recreational mathematics and shown three puzzles, which all relates to the \rubik{}; \msquare{}, \mcube{} and \mpuzzle{}. The \msquare{} was the predecessor to \mcube{}, which is in turn the predecessor to the \rubik{}. The permutation from the \mpuzzle{} inspired the creation of \rubik{}, which uses a similar principle for moving the \cpiece{}s around.}