\chapter{Beginner's Algorithm}\label{chap:beginnerImplement}
\myTop{In this chapter the process of implementing beginner's algorithm, which is described in section \ref{sec:beginner}, will be presented.
This implementation will not be as effective as beginner's algorithm is capable of since it is a proof of concept.
How efficient it is will be presented in form of statistics about the number of twists it needs to solve the Rubik's Cube.}
This chapter is divided into the different steps used in the beginner's algorithm.
Each step is using different algorithms which all are generally structured in the same way. 

For the sake of simplicity the first layer (down face) in our implementation will always be the same face. We have chosen that face to be the yellow face, the green is the front face, and the red is the right face. This will make the implementation process easier, but the solution will require more twists since it is unlikely that the yellow face is the optimal choice as the first layer face for every solve.

The implementation uses several algorithms which all are named algorithm XnN, where Xn is the step that the algorithm is used in and N is used to distinguish the algorithms from each other, which are used in the same step.

Most of them contains a \textbf{switch-case} statement which is dependent on some input specified for each algorithm. In all cases this is based on the point of view. Normally a human will simply rotate the whole \cube{} and perform the same algorithm, but we found it easier simply to define the algorithms from the different locations.

\section{The Steps}
In the following the implementation of the steps of the beginner's algorithm will be described.
The steps are based on the steps described in section \ref{sec:beginner}. 
\subsection{Step 1 -- Getting the Cross}
\input{input/implementation/beginnersAlg/step1}
\subsection{Step 2 -- Completing the First Layer}
\input{input/implementation/beginnersAlg/step2}
\subsection{Step 3 -- Solving the Second Layer}
\input{input/implementation/beginnersAlg/step3}
\subsection{Step 4a --  Getting the Last Layer Cross}
\input{input/implementation/beginnersAlg/step4}
\subsection{Step 4b -- Completing the Last Layer Cross}
\input{input/implementation/beginnersAlg/step5}
\subsection{Step 5a -- Positioning the Last Layer Corners}
\input{input/implementation/beginnersAlg/step6}
\subsection{Step 5b -- Completing the Last Layer}
\input{input/implementation/beginnersAlg/step7}

\section{Twist Reduction}
As mentioned before our implementation of the beginner's algorithm is not as efficient as it can be. We can however take some steps towards improving its efficiency. One of these steps is removing unnecessary moves and replacing a move sequence with a shorter move sequence, which gives the same result.

An unnecessary move sequence can be performing a twist and just after that twist perform its inverse move. e.g. performing \m{U U'} or \m{U' U}.
According to the theory of groups in section \ref{sec:groupDefinition} two moves, which are each other's inverse give the same result as not performing the two moves.

It was necessary to be able to shorten the twists generally, so any move sequence can not be replaced with a shorter one in our program.
An example of replacing a move sequence with a shorter one generally is replacing three of the same type of move with a single inverse move of that type. e.g. \m{U U U} also noted as \m{U2 U} or \m{U U2} can be replaced with a single inverse move \m{U'}. This is also described in the group theory section \ref{sec:groupDefinition}.

\input{input/implementation/beginnersAlg/effeciency}

\myTail{In this chapter the implementation of beginner's algorithm is described.
Statistics about our implementation is gathered in order to compare this algorithm to our implementation of Kociemba's optimal solver.}